Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-01 doc/PRF2022/PRF_main.tex
conclusion 1st draft

The characteristics of the self-assembly of amphiphilic JP into onion-like
dendrimersomes have been studied
by molecular dynamics simulations~\cite{C9NR05885K}.  
The molecular dynamics simulations
use an anisotropic pair potential
is used to describe the particle interactions
where a harmonic form describes the repulsive part 
and an anisotropic attractive part describes the hydrophobic interactions.
\section{Conclusion}

\label{sec:conclusion}

@@

>>>>

The characteristics of the self-assembly of amphiphilic JP into onion-like
dendrimersomes have been studied
by molecular dynamics simulations~\cite{C9NR05885K}.  
The molecular dynamics simulations
use an anisotropic pair potential
is used to describe the particle interactions
where a harmonic form describes the repulsive part 
and an anisotropic attractive part describes the hydrophobic interactions.

\section{Conclusion}
\label{sec:conclusion}

In this work, we employ the newly developed JP model using BIEs and tune 
the boundary conditions with energy normalization to study the dynamics of 
amphiphilic and dipolar like JPs. The normal derivative \eqref{eq:normal_deriv} 
overcomes an obstacle for numerical implementations in the free energy $F$ 
where the gradient of solution to the screened Laplace equation involves 
hyper-singularities.

Simulations include the self-assembly behaviors when the flow is absent and 
particle aggregations when suspended in shear and TG background flows with 
various flow rates. We track the total free energy, the orientational order 
parameter, and the strain parameter to comprehensively summarize and classify 
the effective properties of all three materials. Observations have shown that 
multi-lamella and the striated structures Under a relatively weak linear shear flow 
behave like a rigid body with minimal deformation. The effective viscosity of the 
material gives a quantitative validation to support the statement. High shear rate 
cases provide the range when the critical shear rate for structure to break apart 
and major topological changes. As expected in all case studies, the free energy 
spikes at certain levels are indicators.

Under a TG flow, we examine the same measures and simulate all structures with 
the same criteria as ones in shear flow cases. In addition, for JP vesicle under a 
TG flow, we compare the results when the size of cell is varied and a nonmonotonic 
trend in reduced area with respect to the cell size arises.

The results reported here provide a preliminary framework for colloidal sciences. 
The present study also helps us to understand more rheological properties of industrial 
produced Janus particles. This study can be extended to three dimensional system 
and it has been included in our future goals. The boundary condition can be designed 
as one with random perturbations that are more close to lab experiments.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
